Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-04-26 paper.tex
edits in Sect 2.2

\definecolor{mygreen}{rgb}{0.,0.5,0.}
\def\del#1{{}}
%\def\del#1{{\bf (DELETED TEXT)}}
\def\C#1{{\bf #1}}
\def\AP#1{{\bf  AP: #1}}
\def\APP#1{{\bf {\color{blue} AP2: #1}}}
\def\SPO#1{{\bf {\color{red} SPO: #1}}}
\def\CP#1{{\bf {\color{mygreen} CP: #1}}}

@@

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm Coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|{{dp}\over{dt}}\right|_{\rm rad}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (rad) and Coulomb (Coul)
losses, $D_{pp}$ is the momentum space diffusion coefficient, and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM. The first term containing the expression
$\bnabla\bcdot \bvel$ represents Fermi-I acceleration and the second
term of this form describes adiabatic gains and losses.

@@

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
\lefteqn{
  {{d f_{\rmn{p}}(p,t)}\over{d t}} =
  {{\partial }\over{\partial p}}
  \left\{
  f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm Coul}
    + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
\nonumber\\
&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
- \bvel_{\rmn{st}}\bcdot\bnabla f_{\rmn{p}}(p,t)
\nonumber\\
&&+\,\,\, {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $\bvel_{\rmn{st}}=-\varv_{\rmn{A}}\bnabla f_{\rmn{p}}/|\bnabla
f_{\rmn{p}}|$ is the streaming velocity in the isotropic transport
approximation, $\varv_{\rmn{A}}$ is the Alfv\'en speed,
$Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
CRps as a function of momentum $p$ and time $t$, and $\tau_{\rm had}$
is the timescale of hadronic losses that produce pions via CRp
collisions with thermal protons of the ICM \cite[e.g.][]{brunetti11}.

\subsection{Turbulent reacceleration}
We incorporate momentum diffusion for electrons and protons via the
transit-time-damping (TTD) resonance with compressible MHD turbulence,
to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
TTD resonance requires the wave frequency to obey the resonance
condition, $\omega=k_\parallel\varv_\parallel$, where $k_\parallel$
and $\varv_\parallel$ are the parallel (projected along the magnetic
field) wavenumber and particle velocity, respectively. This implies
that the particle transit time across the confining wave region
matches the wave period,
$\lambda_{\parallel}/v_{\parallel}=\tau_{\rmn{wave}}$. Note, the CRs'
gyroradius does not enter the resonance condition. Hence the CRs that
are in resonance with compressible waves experience Fermi-II
acceleration irrespectively of the length scale of the perturbation.

However, the resonance changes the component of the particle momentum
parallel to the mean magnetic field, which over time leads to
increasing anisotropy in the particle distribution that decreases the
efficiency of reacceleration with time. As in \citet{brunetti11}, we
assume that there exists a mechanism---such as the firehose
instability---that isotropizes the CR distribution function at the
gyroscale and on the reacceleration time scale, which ensures
sustained efficient reacceleration with time.
\CP{add OoM}

The particle pitch-angle averaged momentum-diffusion coefficient of
isotropic particles that couple to fast magnetosonic modes via TTD
resonance is \citep[][ Eqn. 47]{brunetti07}:
\begin{eqnarray}
  D_{pp}(p,t) = \frac{\upi}{16} \frac{p^2}{\rho c}
  \left\langle\frac{\beta |B_k|^2}{16 \upi \,W}\right\rangle
  I_\theta
  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
\label{eq:dpp}
\end{eqnarray}
where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
is the speed of light. The energy density $W$ of a mode in a
magnetized plasma stems from both electromagnetic fields and resonant
particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
beta-weighted magnetic-to-total energy density saturates to $\langle\beta
|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
\citealt{brunetti07}). The pitch angle of the CR momentum with the
magnetic field orientation is given by $\theta$, and
\begin{equation}
  \label{eq:I_theta}
  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
    |\cos \theta | }}
\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
\end{equation}
Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
in \cite{brunetti07}, we initially assume that the velocity of
turbulent eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the
cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
Tab.~\ref{tab:timescales} for more details).

@@

The profile of injected turbulence depends on the details of the
merger such as time during the merger, the impact parameter, the
merger mass ratio, and the degree of cluster anisotropy
\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
assume that it scales with the thermal energy density to some
power. Hence we assume volumetric injection rate of turbulent energy,
$I_0\propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
normalization by requiring that the turbulent energy in compressible
modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
radio halo.\footnote{Simulations show that the compressible modes
  contribute a factor $0.2-0.4$ to the total turbulent energy
  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
  total turbulent energy, which can be decomposed into a slenoidal and
  compressible component, is typically $\sim15-70$\% of the thermal
  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
  our adopted value of $X_\rmn{tu}$.} In this work we investigate
different spatial models for injected turbulence. With the above
choice of normalization, the turbulent energy density becomes
$\epsilon_\rmn{turb} \propto
\epsilon_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
\Mprimary (see Figure~\ref{fig:turb} for visualization).

@@

For reference we show in Table~\ref{tab:timescales} both the thermal
quantities and the timescales for CR cooling and (re)acceleration for
three different spatial regions of the RH. Interestingly the
reacceleration timescale $\tau_D$ is similar between our three models,
where the difference comes from turbulent profile parameterized with
$\alpha_\rmn{tu}$. This implies that even small differences in the
turbulent profile could impact the seed CRs significantly.

@@

We adopt both the density \citep{1992A&A...259L..31B} and temperature
profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,.
\end{eqnarray}
The virial and core radii of Coma are given by $R_{200} =
2300\,\rmn{kpc}$ and $R_{\rmn{c}} = 294\,\rmn{kpc}$, respectively.
The bulk of the CRps are injected by relatively low Mach number shocks
and parameterized by $f_\rmn{CRp,inj}(p) =
C_\rmn{CRp,inj}\,p^{-2.5}$. The CRps trace the thermal gas with
$C_\rmn{CRp,inj} \propto \epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$,
where the normalization is fixed by assuming that the injected CR
energy in the last 650~Myrs make up 0.03\% of the thermal energy
inside the virial radius, i.e.
$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj} \rmn{d}
V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{CRp,0} \propto \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalization by requiring
$\int_0^{R_{200}}\epsilon_\rmn{CRp,0}
\rmn{d}V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
0.003$. Similarly, the initial CRe distribution is given by the steady
state between cooling (Coulomb, inverse Compton, and synchrotron) and
injection of secondary CRes from $f_{CRp,0}$. We also include the
continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
compressible turbulence responsible for reaccelerating both the CRps
and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_e
T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
calculated for each radial bin using
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
are similar to what is used for our simulated cluster.

\subsection{Cosmological simulation methodology}
In this paper we focus on our simulated cluster, g72a, which is a
massive $1.6\times10^{15}\,M_\odot$ cluster that experienced a merger
about 1-2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster
mass, density and temperature profiles are all similar to the well
studied Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will
compare our calculations to radio and gamma-ray observations of Coma.

>>>>

\definecolor{mygreen}{rgb}{0.,0.5,0.}
\def\del#1{{}}
%\def\del#1{{\bf (DELETED TEXT)}}
\def\C#1{{\bf #1}}
\def\AP2#1{{\bf  AP2: #1}}
\def\AP#1{{\bf {\color{blue} AP: #1}}}
\def\SPO#1{{\bf {\color{red} SPO: #1}}}
\def\CP#1{{\bf {\color{mygreen} CP: #1}}}

@@

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|\frac{dp}{dt}\right|_{\rm Coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|\frac{dp}{dt}\right|_{\rm rad}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (rad) and Coulomb (Coul)
losses, \AP{please insert formulae:}
\begin{eqnarray}
  \left|\frac{dp}{dt}\right|_{\rm Coul}
  &=& \\
  \left|\frac{dp}{dt}\right|_{\rm rad~}
  &=& 
\end{eqnarray}
$D_{pp}$ is the momentum space diffusion coefficient (see
Sect.~\ref{sec:reacc}), and $Q_{\rmn{e}}$ denotes the injection rate
of primary and secondary electrons in the ICM (see
Sect.~\ref{sec:cosmo_sim}). The first term containing the expression
$\bnabla\bcdot \bvel$ represents Fermi-I acceleration and the second
term of this form describes adiabatic gains and losses.

@@

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
\lefteqn{
  {{d f_{\rmn{p}}(p,t)}\over{d t}} =
  {{\partial }\over{\partial p}}
  \left\{
  f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm Coul}
    + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
\nonumber\\
&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
- \bvel_{\rmn{st}}\bcdot\bnabla f_{\rmn{p}}(p,t)
\nonumber\\
&&+\,\,\, {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $\bvel_{\rmn{st}}=-\varv_{\rmn{A}}\bnabla f_{\rmn{p}}/|\bnabla
f_{\rmn{p}}|$ is the streaming velocity in the isotropic transport
approximation, $\varv_{\rmn{A}}$ is the Alfv\'en speed,
$Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
CRps as a function of momentum $p$ and time $t$ (see
Sect.~\ref{sec:cosmo_sim}), and $\tau_{\rm had}$ is the timescale of
hadronic losses that produce pions via CRp collisions with thermal
protons of the ICM \cite[e.g.][]{brunetti11}.
\AP{please insert formulae:}
\begin{eqnarray}
  \tau_{\rm had} = 
\end{eqnarray}

\subsection{Turbulent reacceleration}
\label{sec:reacc}

We incorporate momentum diffusion for electrons and protons via the
transit-time-damping (TTD) resonance with compressible MHD turbulence,
to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
TTD resonance requires the wave frequency to obey the resonance
condition, $\omega=k_\parallel\varv_\parallel$, where $k_\parallel$
and $\varv_\parallel$ are the parallel (projected along the magnetic
field) wavenumber and particle velocity, respectively. This implies
that the particle transit time across the confining wave region
matches the wave period,
$\lambda_{\parallel}/v_{\parallel}=\tau_{\rmn{wave}}$. Note, the CRs'
gyroradius does not enter the resonance condition. Hence the CRs that
are in resonance with compressible waves experience Fermi-II
acceleration irrespectively of the length scale of the perturbation.

However, the resonance changes the component of the particle momentum
parallel to the mean magnetic field, which over time leads to
increasing anisotropy in the particle distribution that decreases the
efficiency of reacceleration with time. As in \citet{brunetti11}, we
assume that there exists a mechanism---such as the firehose
instability---that isotropizes the CR distribution function at the
gyroscale and on the reacceleration time scale, which ensures
sustained efficient reacceleration with time.

\SPO{please check the following:} To order of magnitude, the
momentum-space diffusion coefficient due to second-order Fermi-II
acceleration scales as
\begin{eqnarray}
  D_{pp} \propto p\dot{p}
  \propto p^2\langle kc\rangle_{\mathcal{W}} \left(\frac{\Vph}{c}\right)^2,
\label{eq:dpp_oom}
\end{eqnarray}
since the force on a particle due to Fermi-II acceleration scales as
$\dot{p}\sim p/\tau\sim p \langle kc\rangle_{\mathcal{W}} (\Vph/c)^2$
where $\langle kc\rangle_{\mathcal{W}} (\Vph/c)^2$ is the wave
energy-averaged wave-particle interaction rate. It can be shown that
the particle pitch-angle averaged momentum-diffusion coefficient of
isotropic particles that couple to fast magnetosonic modes via TTD
resonance is \citep[][ Eqn. 47]{brunetti07}:
\begin{eqnarray}
  D_{pp}(p,t) = \frac{\upi}{16} \frac{p^2}{\rho c}
  \left\langle\frac{\beta |B_k|^2}{16 \upi \,W}\right\rangle
  I_\theta
  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
\label{eq:dpp}
\end{eqnarray}
where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
is the speed of light. The energy density $W$ of a mode in a
magnetized plasma stems from both electromagnetic fields and resonant
particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
beta-weighted magnetic-to-total energy density saturates to $\langle\beta
|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
\citealt{brunetti07}). The pitch angle of the CR momentum with the
magnetic field orientation is given by $\theta$, and
\begin{equation}
  \label{eq:I_theta}
  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
    |\cos \theta | }}
\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
\end{equation}
Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
in \cite{brunetti07}, we initially assume that the velocity of
turbulent eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the
cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
Tab.~\ref{tab:timescales} for more details).

@@

The profile of injected turbulence depends on the details of the
merger such as time during the merger, the impact parameter, the
merger mass ratio, and the degree of cluster anisotropy
\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
assume that it scales with the thermal energy density to some
power. Hence we assume volumetric injection rate of turbulent energy,
$I_0\propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
normalization by requiring that the turbulent energy in compressible
modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
radio halo.\footnote{Simulations show that the compressible modes
  contribute a factor $0.2-0.4$ to the total turbulent energy
  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
  total turbulent energy, which can be decomposed into a slenoidal and
  compressible component, is typically $\sim15-70$\% of the thermal
  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
  our adopted value of $X_\rmn{tu}$.} In this work we investigate
different spatial models for injected turbulence. With the above
choice of normalization, the turbulent energy density becomes
$\epsilon_\rmn{turb} \propto
\epsilon_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
\Mprimary (see Figure~\ref{fig:turb} for visualization). \CP{These
  models and scaling indices are not well motivated here, they would
  better fit into the results section.}

@@

\SPO{this needs a rewrite in the light of an updated discussion of
  $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$.}  For reference we show in
Table~\ref{tab:timescales} both the thermal quantities and the
timescales for CR cooling and (re)acceleration for three different
spatial regions of the RH. Interestingly the reacceleration timescale
$\tau_{\rm D}$ is similar between our three models, where the
difference comes from turbulent profile parameterized with
$\alpha_\rmn{tu}$. This implies that even small differences in the
turbulent profile could impact the seed CRs significantly.

@@

We adopt both the density \citep{1992A&A...259L..31B} and temperature
profiles \citep{2009ApJ...696.1886B,2001A&A...365L..67A} derived from
X-ray observations of the Coma cluster. They are given by:
\begin{eqnarray}
n_e &=& \frac{3.4\times10^{-3}}{\left[1+\left(R/R_{\rmn{c}}\right)^2\right]^{1.125}}\nonumber\\
k_{\rmn{B}} T &=& 8.25\,\rmn{keV} \left[1+\left(2R/R_{200}\right)^2\right]^{-0.32}\,.
\end{eqnarray}
The virial and core radii of Coma are given by $R_{200} =
2300\,\rmn{kpc}$ and $R_{\rmn{c}} = 294\,\rmn{kpc}$, respectively.
The bulk of the CRps are injected by relatively low Mach number shocks
and parameterized by $f_\rmn{CRp,inj}(p) =
C_\rmn{CRp,inj}\,p^{-2.5}$. The CRps trace the thermal gas with
$C_\rmn{CRp,inj} \propto \epsilon_\rmn{th}^{\alpha_\rmn{CR,spat}}$,
where the normalization is fixed by assuming that the injected CR
energy in the last 650~Myrs make up 0.03\% of the thermal energy
inside the virial radius, i.e.
$\int_0^{R_{200}}\epsilon_\rmn{CRp,inj} \rmn{d}
V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{CRp,0} \propto \frac{\int_p^\infty f_\rmn{CRp,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalization by requiring
$\int_0^{R_{200}}\epsilon_\rmn{CRp,0}
\rmn{d}V\left(\int_0^{R_{200}}\epsilon_\rmn{th} \rmn{d}V\right)^{-1} =
0.003$. Similarly, the initial CRe distribution is given by the steady
state between cooling (Coulomb, inverse Compton, and synchrotron) and
injection of secondary CRes from $f_{CRp,0}$. We also include the
continuous injection of secondary CRes during $\tau_\rmn{cl}$. The
compressible turbulence responsible for reaccelerating both the CRps
and CRes is parameterized by $I_0 \propto X_\rmn{tu} (n_{\rmn{e}}
T)^{\alpha_\rmn{tu}}$. The diffusion constant $D_\rmn{pp}$ is
calculated for each radial bin using
Eqns.~\ref{eq:dpp}-\ref{eq:Gamma_e}. All parameters and assumptions
are similar to what is used for our simulated cluster.

\subsection{Cosmological simulation methodology}
\label{sec:cosmo_sim}
In this paper we focus on our simulated cluster, g72a, which is a
massive $1.6\times10^{15}\,M_\odot$ cluster that experienced a merger
about 1-2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster
mass, density and temperature profiles are all similar to the well
studied Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will
compare our calculations to radio and gamma-ray observations of Coma.
